\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-06-05 trunk/final-version/europa.tex
Final Version to be sent to Publisher

\begin{figure}[b]
\centering
\includegraphics[scale=2.5]{figs/EUROPA-Architecture.jpeg}
\caption{\small The \eu software architecture.}
\label{fig:europa-architecture}
\end{figure}

@@

\kcomment{Fig. \ref{fig:nddllight} is a \nd (covered in more detail in
  Section \ref{sec:europa:modeling}) model of a light bulb and a
  switch that controls it along with a problem instance that requires
  the light bulb to be \texttt{off} by time$=10$, given an initial
  state with the bulb \texttt{on} at time$=0$. The \nd module allows
  \eu to ingest this model and the problem description. Once the \nd
  statements are parsed, different object types, object instances and
  constraints are instantiated inside the \texttt{PDB} and
  \texttt{CRE} modules where they are available for the user and the
  solver modules to query and manipulate programmatically. This
  instantiation of the initial state constitutes the initial plan that
  \eu holds for this particular problem instance.

@@

\begin{figure}[!htb]
  \centering
  \subfloat[\small A Simple Temporal Network (\texttt{STN}). \kcomment{Nodes correspond
  to variables and their domains and arc's the \emph{constraint} or
  distance between them.}]{\label{fig:stn1}\includegraphics[width=0.5\columnwidth]{figs/stn-graph.jpeg}}
  \subfloat[\small The resulting distance graph from \ref{fig:stn1}.]{\label{fig:stn2}\includegraphics[width=0.5\columnwidth]{figs/distance-graph.pdf}}
  \caption{\small An illustration of a \texttt{STN} and its
    corresponding distance graph.}
  \label{fig:stn}
\end{figure}

@@

\begin{algorithm}
\KwIn{PartialPlan $plan$}
\KwOut{\texttt{true} if a plan solution was found, \texttt{false} otherwise}
\Begin{
  \lIf{isInconsistent(plan)}{\Return \texttt{false}\;}\label{li:propagate}
  \BlankLine
  Flaw $flaw \leftarrow chooseFlaw(plan)$ \; \label{li:selectflaw}
  \lIf{ $\emptyset = flaw$ }{\Return \texttt{true} \;} \label{li:noflaw}
  \BlankLine
  DecisionPoint $decision \leftarrow makeDecisionPoint(flaw, plan)$ \comment{\{\emph{potential branching point(s)}\}}\;\label{li:decisionpt}
  \While{ $decision.hasNext()$ }{ \label{li:decisionloop}
    PartialPlan $pp \leftarrow decision.executeNext()$ \; \label{li:decide}
    \lIf{ $solve(pp)$ }{ \Return \texttt{true} \; } \label{li:recurse}
    \lElse{ $decision.undo()$ \comment{\{\emph{possible backtracking point}\}}\; } \label{li:backtrack}
   }
   \Return \texttt{false} \; \label{li:noplan}
 }
\caption{$\mathrm{bool} ~ solve(plan)$\kcomment{: To deliberate and
    generate partial plans}}
\label{alg:europa:solve}
\end{algorithm}

>>>>

\begin{figure}[b]
\centering
\includegraphics[scale=0.5]{figs/EUROPA-Architecture.jpeg}
\caption{\small The \eu software architecture.}
\label{fig:europa-architecture}
\end{figure}

@@

\kcomment{Fig. \ref{fig:nddllight} is a \nd model (covered in more
  detail in Section \ref{sec:europa:modeling}) of a light bulb and a
  switch that controls it along with a problem instance that requires
  the light bulb to be \texttt{off} by time $=10$, given an initial
  state with the bulb \texttt{on} at time $=0$. The \nd module allows
  \eu to ingest this model and the problem description. Once the \nd
  statements are parsed, different object types, object instances and
  constraints are instantiated inside the \texttt{PDB} and
  \texttt{CRE} modules where they are available for the user and the
  solver modules to query and manipulate programmatically. This
  instantiation of the initial state constitutes the initial plan that
  \eu holds for this particular problem instance.

@@

\begin{figure}[!htb]
  \centering
  \subfloat[\small A Simple Temporal Network (\texttt{STN}). \kcomment{Nodes correspond
  to variables and their domains and arc's the \emph{constraint} or
  distance between them.}]{\label{fig:stn1}\includegraphics[width=0.5\columnwidth]{figs/stn-graph.jpeg}}
  \subfloat[\small The resulting distance graph from \ref{fig:stn1}.]{\label{fig:stn2}\includegraphics[width=0.5\columnwidth]{figs/distance-graph.jpeg}}
  \caption{\small An illustration of a \texttt{STN} and its
    corresponding distance graph.}
  \label{fig:stn}
\end{figure}

@@

\begin{algorithm}
\KwIn{PartialPlan $plan$}
\KwOut{\texttt{true} if a plan solution was found, \texttt{false} otherwise}
\Begin{
  \lIf{isInconsistent(plan)}{\Return \texttt{false}\;}\label{li:propagate}
  \BlankLine
  Flaw $flaw \leftarrow chooseFlaw(plan)$ \; \label{li:selectflaw}
  \lIf{ $\emptyset = flaw$ }{\Return \texttt{true} \;} \label{li:noflaw}
  \BlankLine
  DecisionPoint $decision \leftarrow makeDecisionPoint(flaw, plan)$ \tcp*{potential branching point(s)};\label{li:decisionpt}
  \While{ $decision.hasNext()$ }{ \label{li:decisionloop}
    PartialPlan $pp \leftarrow decision.executeNext()$ \; \label{li:decide}
    \lIf{ $solve(pp)$ }{ \Return \texttt{true} \; } \label{li:recurse}
    \lElse{ $decision.undo()$ } ;// \texttt{possible backtracking point}\ \label{li:backtrack}
   }
   \Return \texttt{false} \; \label{li:noplan}
 }
\caption{$\mathrm{bool} ~ solve(plan)$\kcomment{: To deliberate and
    generate partial plans}}
\label{alg:europa:solve}
\end{algorithm}
